{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-15 brains-introduction.tex
Update state of the art on network studies

Less classical linguistic variables, based on the study of semantic network properties, have recently started to be used, in the context of connectionism and its normative processual models (see for instance \citet{collins1975spreading} for an example of such models).
Let us mention two interesting studies on that matter, which demonstrate in a strictly \emph{in vitro} framework and at the vocabulary level that word properties computed on a word network are important factors for the cognitive processes and reproduction of those words.
First, \citet{Griffiths07} analyze a task where subjects are asked to name the first word which comes to their mind when they are presented with a random letter from the %Latin
alphabet. The authors show that there exists a link between the ease of recall of words and one of their semantic features, namely their authority position (PageRank) in a language-wide semantic network built from external word association data.
A second psycholinguistic study by \citet{Chan10} shows, in a picture-naming task, that words are produced faster and with fewer mistakes when they have a lower clustering coefficient in an underlying phonological network (which, again, is  defined from external phonological data).
\rk{add \url{https://www.sciencedirect.com/science/article/pii/S0893608012000330}, \url{http://research.clps.brown.edu/austerweil/pdfs/papers/randomWalkNips2012.pdf}, \url{http://link.springer.com/article/10.3758/s13421-013-0312-y} to that picture}

>>>>

Less classical linguistic variables, based on the study of semantic network properties, have recently started to be used, in the context of connectionism and its normative processual models (see for instance \citet{collins1975spreading} for an example of such models).
Let us mention four interesting studies on that matter, which demonstrate in a strictly \emph{in vitro} framework and at the vocabulary level that word properties computed on a word network are important factors for the cognitive processes and reproduction of those words.
First, \citet{Griffiths07} analyze a task where subjects are asked to name the first word which comes to their mind when they are presented with a random letter from the %Latin
alphabet. The authors show that there exists a link between the ease of recall of words and one of their semantic features, namely their authority position (pagerank) in a language-wide semantic network built from external word association data.
\citet{austerweil2012human} further develop this idea by showing that random walk on such a semantic network, i.e. the exact process measured by the pagerank index, gives a parsimonious account of some semantic retrieval effects (namely, related items being retrieved together).
A third psycholinguistic study by \citet{Chan10} shows, in a picture-naming task, that words are produced faster and with fewer mistakes when they have a lower clustering coefficient in an underlying phonological network (which, again, is  defined from external phonological data).
\citet{nelson2013activation}, finally, show the importance of clustering coefficient in a semantic network by studying the role it plays in a variety of recall and recognition tasks (extralist and intralist cuing, single item recognition, and primed free assocation).
